Case Study: scRNA-seq (Mouse data, MAST method)

### 2018-02-27 datasets/scrnaseq/scrnaseq-human-mast.Rmd
Fix typo in dataset name

  # subset by groups of interest
  humandata <- humandata2[, (colData(humandata)$characteristics_ch1.7 %in% 
                         c("neoplastic: Neoplastic", "neoplastic: Regular")) &
                         (colData(humandata)$characteristics_ch1.5 %in% 
                         c("tsne cluster: 11",  "tsne cluster: 8"))]
  cdata=colData(humandata)
  cdata$group <- cdata$characteristics_ch1.7

@@

For the human dataset, there are a total of `r nrow(humandata2)` cells and `r ncol(humandata2)` genes.

>>>>

  # subset by groups of interest
  humandata <- humandata[, (colData(humandata)$characteristics_ch1.7 %in% 
                         c("neoplastic: Neoplastic", "neoplastic: Regular")) &
                         (colData(humandata)$characteristics_ch1.5 %in% 
                         c("tsne cluster: 11",  "tsne cluster: 8"))]
  cdata=colData(humandata)
  cdata$group <- cdata$characteristics_ch1.7

@@

For the human dataset, there are a total of `r nrow(humandata)` cells and `r ncol(humandata)` genes.

### 2018-02-27 datasets/scrnaseq/scrnaseq-mouse-mast.Rmd
Fix typo in dataset name

  # subset by genes not all zero
  mousedata <- mousedata2[rowSums(assays(mousedata)[["count"]]==0) < ncol(mousedata),]

  # look at number of cells in each group
  table(as.character(colData(mousedata2)$group))

@@

For the mouse dataset2, we have a total of `r ncol(mousedata2)` cells and 
`r nrow(mousedata2)` genes after filtering for non-detected genes.

>>>>

  # subset by genes not all zero
  mousedata <- mousedata[rowSums(assays(mousedata)[["count"]]==0) < ncol(mousedata),]

  # look at number of cells in each group
  table(as.character(colData(mousedata)$group))

@@

For the mouse dataset2, we have a total of `r ncol(mousedata)` cells and 
`r nrow(mousedata)` genes after filtering for non-detected genes.
